\section{Robustness of MTL formulae}
\label{sec:robust semantics}

Consider a discrete-time dynamical system $\Sys$ given by 
\begin{equation}
\label{eq:xt}
x_{t+1} = f(x_t,u_t)
\end{equation}
where $x \in X \subset \Re^n$ is the state of the system and $u \in U \subset \Re^m$ is its control input.
The system's initial state $x_0$ takes value from some initial set $X_0 \subset \Re^n$.
Given an initial state $x_0$ and a finite control input sequence $\inpSig = (u_0,\ldots, u_{T-1}), u_t \in U$, a \textit{trajectory} of the system is the unique sequence of states $\sstraj = (x_0,\ldots,x_T)$ s.t. for all $t$, $x_t$ is in $X$ and obeys \eqref{eq:xt}.
%We will use $\TDom$ to abbreviate the time domain $\{0,1,2,\ldots\}$.
All temporal intervals that appear in this paper are implicitly discrete-time, e.g. $[a,b]$ means $[a,b] \cap \Ne$. 
The set $\{0,1,\ldots,T\}\subset \Ne$ will be abbreviated as $\TDom$.
For an interval $I \subset \Ne$, let $t+I = \{t+a \such a \in I\}$.
The set of subsets of a set $S$ is denoted $\Pc(S)$.
The signal space $\SigSpace$ is the set of all signals $\sstraj: \TDom \rightarrow X$.
The max operator is written $\sqcup$ and min is written $\sqcap$.

\subsection{Metric Temporal Logic (MTL)}
\label{sec:mtl}
The controller of $\Sys$ is designed to make the closed loop system \eqref{eq:xt} satisfy a specification expressed in MTL~\cite{Ouaknine08_RecentResultsMTL}.
Formally, let $AP$ be a set of atomic propositions, which can be thought of as point-wise constraints on the state of the system.
An MTL formula $\formula$ is built recursively from the atomic propositions using the following grammar:
\[\formula \defeq \top|p|\neg \formula | \formula_1 \land \formula_2 | \formula_1 \until_I \formula_2\]
where $I \subset \Re$ is a time interval.
Here, $\top$ is the Boolean True, $p$ is an atomic proposition, $\neg$ and $\land$ are the Boolean negation and AND operators, respectively, and $\until$ is the Until temporal operator.
Informally, $\formula_1 \until_I \formula_2$ means that $\formula_1$ must hold \textit{until} $\formula_2$ holds, and that the hand-over from $\formula_1$  to $\formula_2$ must happen sometime during the interval $I$.
The disjunction ($\lor$), implication ($\implies$), Always ($\always$) and Eventually ($\eventually$) operators can be defined using the above operators.

Formally, the \textit{pointwise semantics} of an MTL formula define what it means for a system trajectory $\sstraj$ to satisfy the formula $\formula$.
Let $\Oc: AP \rightarrow \Pc(X)$ be an \textit{observation} map for the atomic propositions.
The boolean truth value of a formula $\formula$ w.r.t. the trajectory $\sstraj$ at time $t$ is defined recursively.
\begin{definition}[MTL semantics]
	\label{def:boolean sat}
	\begin{eqnarray*}
		\label{eq:boolean sat}
		(\sstraj,t) \models \top &\Leftrightarrow& \top
		\\
		\forall p \in AP, (\sstraj, t) \; \models_\Oc p &\Leftrightarrow& x_t \in \Oc(p)
		\\
		(\sstraj,t) \models_\Oc \neg \formula&\Leftrightarrow& \neg (\sstraj,t) \models_\Oc \formula
		\\
		(\sstraj,t) \models_\Oc  \formula_1 \land \formula_2&\Leftrightarrow& (\sstraj,t) \models_\Oc \formula_1 \land (\sstraj,t) \models_\Oc \formula_2
		\\
		(\sstraj,t) \models_\Oc \formula_1 \until_I \formula_2 &\Leftrightarrow& \exists t' \in t+I .  (\sstraj,t') \models_\Oc \formula_2  
		\\
		&& \, \land \forall t'' \in (t,t'), \;\; (\sstraj,t'') \models_\Oc \formula_1 
	\end{eqnarray*}
\end{definition}
As $\Oc$ is fixed in this paper, it is dropped from the notation.
We say $\sstraj$ satisfies $\formula$ if $(\sstraj,0) \models \formula$.
\textit{All formulas that appear in this paper have bounded temporal intervals: $ 0\leq \inf I < \sup I < +\infty$.}
To evaluate whether such a formula $\formula$ holds on a given trajectory, only a finite-length prefix of that trajectory is needed.
Its length can be upper-bounded by the \textit{horizon} of $\formula$, $hrz(\formula) \in \Ne$, calculable as shown in~\cite{Dokhanchi14_OnlineMonitoring}. 
For example, the horizon of $\always_{[0,2]}(\eventually_{[2,4]}p)$ is 2+4=6.

\subsection{Robust semantics of MTL}
\label{sec:rob sem}
Designing a controller that satisfies the MTL formula $\formula$\footnote{Strictly, a controller s.t. the closed-loop behavior satisfies the formula.} is not always enough.
In a dynamic environment, where the system must react to new unforeseen events, it is useful to have a margin of maneuverability.
That is, it is useful to control the system such that we \textit{maximize} our degree of satisfaction of the formula.
When unforeseen events occur, the system can react to them without violating the formula.
This degree of satisfaction can be formally defined and computed using the robust semantics of MTL.
Given a point $x \in X$ and a set $A \subset X$, $\dist(x,A) \defeq \inf_{a \in \cl{A}}|x-a|_2$ is the minimum Euclidian distance from $x$  to the closure $\cl{A}$ of $A$.
\begin{definition}[Robustness\cite{FainekosP09tcs}]
	\label{def:robustness estimate}
	The \emph{robustness} of $\varphi$ relative to $\sstraj$ at time $t$ is recursively defined as 
	\begin{eqnarray*}
		\label{eq:robustness estimate}
		\rob_{\top} (\sstraj,t) &=& +\infty
		\\
		\forall p \in AP, \;  \rob_{p} (\sstraj,t) &=& \left \lbrace \begin{matrix}
			\dist(\stPt_t, \stSet \setminus \Oc(p)), &\text{if } \stPt_t \in \Oc(p)
			\\
			-\dist(x_t, \Oc(p)), &\text{if } \stPt_t \notin \Oc(p)						
		\end{matrix} \right.
		\\
		\rob_{\lnot \formula} (\sstraj,t) &=& - \rob_{\formula} (\sstraj,t)
		\\
		\rob_{ \formula_1 \land \formula_2} (\sstraj,t) &=& \rob_{\formula_1} (\sstraj,t) \sqcap \rob_{\formula_2} (\sstraj,t) 
		\\
		\rob_{ \formula_1 \until_I \formula_2} (\sstraj,t) &=& \sqcup_{t' \in t+_{\TDom}I} \left(\rob_{\formula_2} (\sstraj,t') \bigsqcap \right.
		\\
		&& \left. \sqcap_{t'' \in [t,t')}   \rob_{\formula_1} (\sstraj,t'') \right) 
	\end{eqnarray*}
	When $t=0$, we write $\robf(\sstraj)$ instead of $\robf(\sstraj,0)$.
\end{definition}
The robustness is a real-valued function of $\sstraj$ with the following important property.
\begin{theorem} \cite{FainekosP09tcs}
	\label{thm:rob objective}
	For any $\sstraj \in \SigSpace$ and MTL formula $\formula$, 
	if $\robf(\sstraj,t) <0$ then $\sstraj$ violates the spec $\formula$ at time $t$, and if $\robf(\sstraj,t) > 0$ then $\sstraj$ satisfies $\formula$ at $t$. 
	The case $\robf(\sstraj,t) =0$ is inconclusive.
\end{theorem} 

Thus, we can compute control inputs by maximizing the robustness over the set of finite input sequences of a certain length.
The obtained sequence $\inpSig^*$ is valid if $\robf(\sstraj,t)$ is positive, where $\sstraj$ and $\inpSig^*$ obey \eqref{eq:xt}.
The larger $\robf(\sstraj,t)$, the more robust is the behavior of the system: intuitively, $\sstraj$ can be disturbed and $\robf$ might decrease but not go negative.
