\documentclass[letterpaper, 10pt, conference]{ieeeconf}

% To compress the paper
%\addtolength{\textheight}{1ex}
%\addtolength{\voffset}{-.5ex}
% \renewcommand\topfraction{0.85}
% \renewcommand\bottomfraction{0.85}
% \renewcommand\floatpagefraction{0.85}

\usepackage{fixltx2e}
\usepackage[protrusion=true,expansion=true]{microtype}


\IEEEoverridecommandlockouts        % This command is only needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\input{preamble}

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

%
% \LARGE \bf
%\title{Co-design of Anytime Computation and Control for Cyber Physical Systems}
%\title{Robust Model Predictive Control of Cyber Physical Systems with Anytime Estimation}
%\title{Co-design of Anytime Estimation and Control for Cyber Physical Systems}
\title{Robust Model Predictive Control with Anytime Estimation}

\author{Truong~X.~Nghiem, Yash~V.~Pant and Rahul~Mangharam \\
Department of Electrical and Systems Engineering\\ University of Pennsylvania
\\ \{nghiem, yashpant, rahulm\}@seas.upenn.edu %
\thanks{This work was supported by STARnet -- a Semiconductor Research Corporation program sponsored by MARCO and DARPA -- and %also funded 
by the US Department of Transportation University Transportation Center Program.}
%\thanks{This material is based upon work supported by the DoE Energy Efficient Buildings (EEB) HUB sponsored by the U.S. Department of Energy under Award Number DE-EE0004261.}}
}


\begin{document}
%\bstctlcite{IEEEexample:BSTcontrol}
\maketitle

\begin{abstract}
With an increasing autonomy in modern control systems %a developing trend is that there is a a huge
comes an increasing amount of sensor data to be processed, leading to overloaded computation and communication in the systems.
For example, a vision-based robot controller processes large image data from cameras at high frequency to observe the robot's state in the surrounding environment, which is used to compute control commands.
In real-time control systems where large volume of data is processed for feedback control, the data-dependent state estimation can become a computation and communication bottleneck, resulting in potentially degraded control performance.
%Consequently, designs of such systems where either speed or accuracy of the estimator is the main criteria and this can result in degraded control performance in many cases.
Anytime algorithms, which offer a trade-off between execution time and accuracy of computation, can be leveraged in such systems.
We present a Robust Model Predictive Control approach with an Anytime State Estimation Algorithm, % for closed loop control in overloaded systems. Our control algorithm
which computes both the optimal control signal for the plant and the (time-varying) deadline/accuracy constraint for the anytime estimator.
Our approach improves the system's performance (concerning both the control performance and the estimation cost) over conventional controllers, which are designed for and operate at a fixed computation time/accuracy setting.
We numerically evaluate our approach in an idealized motion model for navigation with both state and control constraints.
\end{abstract}

\section{Introduction}
\input{intro}

\section{Related Work} \label{sec:related}
\input{related}

\section{System Model} \label{sec:model}
\input{model}

\section{Robust MPC with Anytime Estimation}
\label{sec:RMPC}%change section name?
\input{anytime_rmpc}

\section{Robust MPC Formulation}
\label{sec:RMPC-Formulation}
\input{rmpc_formulation}

\section{Implementation Details} \label{sec:implementation}
\input{implementation}

%\section{Necessary Feasibility Condition for RMPC} \label{sec:necessary}
%\input{NecFeas}

\section{Case study} \label{sec:case} %or numerical problem
\input{case}


\section{Conclusions and future work} \label{sec:conclusion}
\input{conclusions}

\appendix


\input{proofFeasibility}

% 
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
%\vspace{-6pt}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,anytime_ref}
%\bibliography{IEEEabrv,references,Case_bib}  % sigproc.bib is the name of the Bibliography in this case

% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
%APPENDICES are optional
%\balancecolumns
%\appendix

%Appendix A
% \section*{Appendix}
% \label{sec:proofs}



\end{document}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
