In this paper we presented an RMPC algorithm for a control system, with state and input constraints, where the state estimator is an anytime algorithm with multiple operation modes.
The modes represent different trade-offs between computation time and estimation accuracy.
The proposed RMPC algorithm computes both the control input to the plant as well as the mode for the anytime estimator. % for the next time step.
%In the RMPC algorithm, 
Robust feasibility and robust satisfiability of the constraints are ensured by tightening the constraints %at time step
corresponding to the estimation mode, and by a terminal set based on robust control invariance.
%The feasibility of the RMPC algorithm, and operation with multiple anytime estimator modes is proved in Theorems \ref{thm:robust-feasible-RMPC}, \ref{thm:robust-feasible-anytime-RMPC} respectively.
As a case study, we applied our scheme to an idealized motion model with three estimation modes and showed the benefits of switching between modes.

Ongoing research focuses on reducing the computational burden of solving the RMPC optimization for each estimation mode at each time step.
This can be achieved by developing conditions that eliminate certain modes which are either infeasible at the current time step or are suboptimal.
Another branch of ongoing work, which is beyond the scope of this paper, is on developing anytime estimators for vision-based control.
This will enable us to apply our approach to real systems.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "CDC14_Anytime_Main"
%%% End: 
